The Next Release Problem in Real World

### 2018-12-17 PaperBody.tex
Experimental set up added

We divided the main part of the report into two parts. First, in section 4, we will organize the requirements in the actual product and create a dataset. And in this process, we're not going to use any random variables, and we're not going to bring in actual profit and cost from the future. 
And in Section 5, we're going to apply different search-based algorithms to the datasets that we've created. In addition to SA, GA, and NSGA2, which were introduced in class, we also implemented IPH and AHP directly and applied them to datasets. We will apply them to actual datasets and compare the performance of each algorithm in terms of time cost and optimization answers. And we'll also see how much search-based algorithm has increased the profit compared to the actual true value.

All codes used in the paper can be found at https://github.com/shkevinlee/CS454

@@

The company always wants to select requirements for the next release to get the highest sum of profits in the limited budget. Let the decision vector $x = \{x_1, x_2, \ldots, x_n\} \in \{0, 1\}$ where $x_i$ is 1 if requirement $i$ is selected and 0 otherwise. Then our objective function can be written as below:
\[
maximize \sum_{i = 1}^{N} profit_i \cdot x_i
\]
subject to
\[
\sum_{i = 1}^{N} cost_i \cdot x_i \leq B
\]
for some bound $B \in \mathbb{Z}^+$ which represents the limited budget.

@@

\section{Algorithms}
We applied two deterministic algorithms(AHP and ILP) and three heuristic algorithms(SA, GA and NSGA-II) which were introduced as the algorithms well-suited for the NRP in papers.\cite{NRP}\cite{ILP}\cite{IGA}\cite{MONRP}

\subsection{greedy algorithm}

@@

\begin{table*}
  \caption{Profit Comparison}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    &eclipse-log&firefox-log&firefox-priority&firefox-comments+priority\\
    \midrule
    Real Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
    \hline
    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
    NSGA-II&3822.47741&13700.52067&16332.6667&28729.33476 \\
    ILP&3825.42768&13768.44722&16336.0&28845.23124 \\
    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
    \bottomrule
  \end{tabular}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\begin{figure*}[h]
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_eclipse_log(comments)_2016meancost.JPG}
\caption{bugzilla-eclipse-log(comments)-2016meancost}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
\caption{bugzilla-firefox-log(comments)-2016meancost}
\label{fig:subim2}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
\caption{bugzilla-firefox-priority-2016meancost}
\label{fig:subim3}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_comments-priority_2016meancost.JPG}
\caption{bugzilla-firefox-comments+priority-2016meancost}
\label{fig:subim4}
\end{subfigure}

\caption{Profit Comparison for each dataset}
\label{fig:image1}
\end{figure*}

@@

\begin{table*}[]
\caption{The sum of profits on each limited budget}
\begin{tabular}{@{}llllll@{}}
\toprule
\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6} 
\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
140,000 & 18948.3466&  \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
220,000 & 25881.1836&  \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
260,000 & 28626.58769& \textbf{28653.54334}& 28161.5672&  28293.21833& 28556.63614\\ \bottomrule
\end{tabular}
\end{table*}

@@

\section{Results}
At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other. In \textbf{table 1}, upper two rows are real cost sum and real profit sum of each datasets. Below these rows, there are maximum profits for each algorithms in four datasets. At the result, every maximum profits are bigger than real profit sum. Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II. \\
\textbf{Figure 1} is the graphs of \textbf{table 1}. Each graph expresses the maximum profit of five algorithms. At the result, the maximum profit of ILP is the biggest, and the maximum profit of NSGA-II and AHP is bigger than the maximum profit of SA and GA in most case. Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA. \\
At experiment 2, we applied four algorithms except NSGA-II to dataset \textit{bugzilla-firefox-comments+priority-2016meancost}. At this experiment, we got the maximum profits while changing the cost constraints. The result is expressed in \textbf{Figure 2} and \textbf{Figure 3}. \textbf{Figure 2} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms. \\
The result is that they are all increasing almost linearly and similarly. One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.
\section{Conclusion}

>>>>

We divided the main part of the report into two parts. First, in section 4, we will organize the requirements in the actual product and create a dataset. And in this process, we're not going to use any random variables, and we're not going to bring in actual profit and cost from the future. 
And in Section 5, we're going to apply different search-based algorithms to the datasets that we've created. In addition to SA, GA, and NSGA2, we also implemented ILH and AHP directly and applied them to datasets. We will apply them to actual datasets and compare the performance of each algorithm in terms of time cost and optimization answers. And we'll also see how much search-based algorithm has increased the profit compared to the actual true value.

All codes used in the paper can be found at

https://github.com/shkevinlee/CS454

@@

The company always wants to select requirements for the next release to get the highest sum of profits in the limited budget. Let the decision vector $\textbf{x} = \{x_1, x_2, \ldots, x_n\} \in \{0, 1\}$ where $x_i$ is 1 if requirement $i$ is selected and 0 otherwise. Then our objective function can be written as below:
\[
maximize \sum_{i = 1}^{N} profit_i \cdot x_i
\]
subject to
\[
\sum_{i = 1}^{N} cost_i \cdot x_i \leq B
\]
for some bound $B \in \mathbb{Z}^+$ which represents the limited budget.

@@

\section{Algorithms}
We applied two deterministic algorithms(AHP and ILP) and three heuristic algorithms(SA, GA and NSGA-II) which were introduced as the algorithms well-suited for the NRP in papers\cite{NRP}\cite{ILP}\cite{IGA}\cite{MONRP}. And, to encourage the performance of heuristic algorithms, we put a greedy solution into the initial population or initial decision vector.

The greedy algorithm for the initial solution of heuristic algorithms is described as below.

\begin{algorithm}
\caption{greedy algorithm}\label{alg:greedy}
\begin{algorithmic}
    \State Let $\textbf{x} = \{0, 0, \ldots, 0\}$ ;
    \State Let $CostSum = 0$ ;
    \For{$i = 1$ to $N$}
        \State $p = argmax(Profit)$ ;
        \If {$CostSum + cost_p \leq B$}
            \State $x_p = 1$ ;
            \State $CostSum = CostSum + cost_p$ ;
        \EndIf
        \State $profit_p = -\infty$ ;
    \EndFor
    \textbf{return} $x$
\end{algorithmic}
\end{algorithm}

@@

\begin{table*}
  \caption{Profit Comparison}
  \label{tab:commands}
  \begin{tabular}{cccccl}
    \toprule
    &eclipse-log&firefox-log&firefox-priority&firefox-comments+priority\\
    \midrule
    Estimated Cost&50699.70190&262945.49581&262945.49581&262945.49581 \\
    Real Profit&3489.63592&13025.88085&12210&26332.88085 \\
    \hline
    SA&3702.85182&13524.93411&16300.0&28358.2295685 \\
    GA&3793.5045&13662.38600&16303.0&28522.11861 \\
    NSGA-II&3822.47741&13700.52067&16332.6667&28729.33476 \\
    ILP& \textbf{3825.42768}&\textbf{13768.44722}&\textbf{16336.0}&\textbf{28845.23124} \\
    AHP&3810.3125825&13758.5577962&16249.0&28811.2749907 \\
    \bottomrule
  \end{tabular}
\label{table:DatasetProfit}
\end{table*}
% end the environment with {table*}, NOTE not {table}!

\begin{figure*}[h]
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_eclipse_log(comments)_2016meancost.JPG}
\caption{bugzilla-eclipse-log(comments)-2016meancost}
\label{fig:subim1}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_log(comments)_2016meancost.JPG}
\caption{bugzilla-firefox-log(comments)-2016meancost}
\label{fig:subim2}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_priority_2016meancost.JPG}
\caption{bugzilla-firefox-priority-2016meancost}
\label{fig:subim3}
\end{subfigure}
\begin{subfigure}{\columnwidth}
\includegraphics[width=0.9\linewidth]{bugzilla_firefox_comments-priority_2016meancost.JPG}
\caption{bugzilla-firefox-comments+priority-2016meancost}
\label{fig:subim4}
\end{subfigure}

\caption{Profit Comparison for each dataset}
\label{fig:DatasetProfit}
\end{figure*}

@@

\begin{table*}[]
\caption{Profit on each limited budget}
\begin{tabular}{@{}llllll@{}}
\toprule
\multicolumn{1}{c}{\multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}The limited\\ budget\end{tabular}}} & \multicolumn{5}{c}{Algorithms}                                                                                                    \\ \cmidrule(l){2-6} 
\multicolumn{1}{c}{}                                                                              & \multicolumn{1}{c}{AHP} & \multicolumn{1}{c}{ILP} & \multicolumn{1}{c}{SA} & \multicolumn{1}{c}{GA} & \multicolumn{1}{c}{NSGA-II} \\ \midrule
100,000 & 14472.21303& \textbf{14530.92923}& 13787.94014& 13916.62496& 14359.51809\\
120,000 & 16798.95935& \textbf{16845.48739}& 16269.28033& 16440.60658& 16746.14339\\
140,000 & 18948.3466&  \textbf{18979.35023}& 18553.36746& 18706.04924& 18906.95215\\
160,000 & 20906.31785& \textbf{20934.94744}& 20559.69749& 20656.69427& 20873.08535\\
180,000 & 22683.10701& \textbf{22718.92665}& 22332.52554& 22449.04724& 22651.51132\\
200,000 & 24343.18852& \textbf{24369.86106}& 23894.25792& 24054.60654& 24281.04096\\
220,000 & 25881.1836&  \textbf{25901.23028}& 25425.18545& 25565.45349& 25804.51079\\
240,000 & 27305.09756& \textbf{27324.51067}& 26790.58789& 26987.08126& 27214.27095\\
260,000 & 28626.58769& \textbf{28653.54334}& 28161.5672&  28293.21833& 28556.63614\\ \bottomrule
\end{tabular}
\label{table:ParetoFront}
\end{table*}

@@

\section{Experimental Set up}
In this section, we describe two experiments for comparing algorithms on datasets and analyzing correlation between cost and profit. We used four datasets(\textit{eclipse, firefox-I, firefox-II} and \textit{firefox-III}) from Bugzilla on experiments which were described in \textbf{section 4}.

At first experiment(EX1), we applied each algorithm to four datasets in order to compare their performances. And we hope to know the effect by different profit strategies through analyzing \textit{firefox-I}, \textit{firefox-II}, and \textit{firefox-III} dataset.

At second experiment(EX2), we applied each algorithm to \textit{firefox-III} dataset to analyze the correlation between cost and profit. And also, we expected to get the interesting range which have a great change as the limted budget are increased or decreased.

All heuristic approaches(SA, GA and NSGA-II) were run for 500,000 function evaluations. The population size was set to 200. So each experimental execution of GA and NSGA-II was terminated when the generation number reached 2,500. GA and NSGA-II used the tournament selection(tournament size is 5), single-point cross-over, and bit-wise mutation for binary-coded GAs. The cross-over probability and the mutation probability were set to 0.8 and 1/N (where N is the length of chromosome same with the number of requirements).

\section{Result and Analysis}
At first experiment, we applied five algorithms to four datasets and compared the maximum profit each other. In \textbf{table \ref{table:DatasetProfit}}, upper two rows are estimated cost sum and real profit sum of each datasets. Below these rows, there are averaged profits for each algorithms on four datasets. At the result, every profits for algorithms are bigger than real profit sum. Also, consumed time to return maximum profit was exceedingly short in ILP and AHP, rather than SA, GA, and NSGA-II.

\textbf{Figure \ref{fig:DatasetProfit}} is the graphs of \textbf{table 1}. Each graph expresses the averaged profit of five algorithms. At the result, the profit of ILP is the biggest, and the profit of NSGA-II and AHP is bigger than SA and GA in most case. Except ILP and AHP, maximum profit is high in order of NSGA-II, GA, then SA.

At experiment 2, we got the profits while changing the cost constraint. The result is expressed in \textbf{Figure \ref{fig:paretofronts}}. \textbf{Figure \ref{fig:paretofronts}} expresses maximum profits on each cost, and \textbf{Figure 3} is integrating graph of \textbf{Figure 2} because of comparing the difference for four algorithms.

The result is that they are all increasing almost similarly. One of the reasons to perform this experiment was that we wondered if there is a peculiar part in cost-profit graph.(if there is exceeding increase in profit) And at the result, there is no prominently peculiar part, and all the results are increasing normally.

\section{Conclusion}
